Simulate Cut Off

### 2022-06-22 simulation_study/simulate_cutoff.Rmd
updating manuscript

Next, item variance heterogeneity was included by manipulating the potential $\sigma$ for each individual item. For small scales, the $\sigma$ = 2 points with a variability of .2, .4, and .8 for low, medium, and high heterogeneity in the variances between items. For the medium scale of data, $\sigma$ = 20 with a variance of 4, 8, and 12. Last, for the large scale of data, $\sigma$ = 350 with a variance of 100, 150, and 200 for heterogeneity.

@@

# medium potential variability 0 to 100 scale
mu2 <- rnorm(30, 50, 10)
sigma1.2 <- rnorm(30, 20, 4)
sigma2.2 <- rnorm(30, 20, 8)
sigma3.2 <- rnorm(30, 20, 12)

# large potential variability in the 1000s scale

mu3 <- rnorm(30, 1000, 150)
sigma1.3 <- rnorm(30, 350, 100)
sigma2.3 <- rnorm(30, 350, 150)
sigma3.3 <- rnorm(30, 350, 200)

while(sum(sigma3.3 < 0) > 0){
  sigma3.3 <- rnorm(30, 350, 200)
}

@@

The first model using original sample size to predict new sample size was significant, `r user_print$full_result$modelfit$r2`, capturing nearly 90% of the variance, `r user_print$estimate$sample_size`. The second model with item standard deviation was better then the first model *F*(`r change_table$df[2]`, `r change_table$res.df[2]`) = `r change_table$statistic[2]`, *p* < .001, `r user_print2$estimate$modelfit$r2`. The item standard deviation predictor was significant, `r user_print2$full_result$sd_item`. The addition of the original pilot sample size was also significant, *F*(`r change_table$df[3]`, `r change_table$res.df[3]`) = `r change_table$statistic[3]`, *p* < .001, `r user_print3$estimate$modelfit$r2`.

@@

The formula for finding the corrected sample size using a 50% decile is: $Final Sample = 0.637 \times X_{Suggested Sample Size} + 0.002 \times X_{SD Items} + -0.546 \times X_{Pilot Sample Size}$.

>>>>

Next, item variance heterogeneity was included by manipulating the potential $\sigma$ for each individual item. For small scales, the $\sigma$ = 2 points with a variability of .2, .4, and .8 for low, medium, and high heterogeneity in the variances between items. For the medium scale of data, $\sigma$ = 25 with a variance of 4, 8, and 16. Last, for the large scale of data, $\sigma$ = 400 with a variance of 50, 100, and 200 for heterogeneity.

@@

# medium potential variability 0 to 100 scale
mu2 <- rnorm(30, 50, 10)
sigma1.2 <- rnorm(30, 25, 4)
sigma2.2 <- rnorm(30, 25, 8)
sigma3.2 <- rnorm(30, 25, 16)

while(sum(sigma3.2 < 0) > 0){
  sigma3.2 <- rnorm(30, 25, 16)
}

# large potential variability in the 1000s scale
mu3 <- rnorm(30, 1000, 150)
sigma1.3 <- rnorm(30, 400, 50)
sigma2.3 <- rnorm(30, 400, 100)
sigma3.3 <- rnorm(30, 400, 200)

while(sum(sigma3.3 < 0) > 0){
  sigma3.3 <- rnorm(30, 400, 200)
}

@@

The first model using original sample size to predict new sample size was significant, `r user_print$full_result$modelfit$r2`, capturing nearly 90% of the variance, `r user_print$estimate$sample_size`. The second model with item standard deviation was better then the first model *F*(`r change_table$df[2]`, `r change_table$res.df[2]`) = `r round(change_table$statistic[2], digits = 2)`, *p* < .001, `r user_print2$estimate$modelfit$r2`. The item standard deviation predictor was significant, `r user_print2$full_result$sd_item`. The addition of the original pilot sample size was also significant, *F*(`r change_table$df[3]`, `r change_table$res.df[3]`) = `r round(change_table$statistic[3], digits = 2)`, *p* < .001, `r user_print3$estimate$modelfit$r2`.

@@

The formula for finding the corrected sample size using a 50% decile is: $Final Sample = 39.269 + 0.700 \times X_{Suggested Sample Size} + 0.003 \times X_{SD Items} + -0.695 \times X_{Pilot Sample Size}$. The suggested sample size will be estimated from the 80%, 85%, 90%, or 95% selection at the 50% decile as shown above. The item SD can be calculated directly from the data, and the pilot sample size is the sample size of the data from which a researcher is simulating their samples.
